Deciding to Disclose

### 2015-07-06 model_description.tex
Add less simple game

To resolve this, we can do exactly that, and cast it as a signalling game. We make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Each of these types of player, will play a different game. This also introduces a third player, who we will call nature. Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform. 
This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome. We must also amend the moves, and payoffs slightly. The woman now claims to be one of the types, and may send a signal to say, for example, that they are a heavy drinker. We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred. We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one (fig \ref{fig:less_simple}).

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=78mm]{figures/less_simple_game}
\end{adjustbox}
\sidecaption{A less simple two player game.}

@@

\begin{figure}[H]
\centering
\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}
\vskip\baselineskip
\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}
\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

>>>>

To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}). We make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Each of these types of player, will play a different game. This also introduces a third player, who we will call nature. Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform. 
This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome. We must also amend the moves, and payoffs slightly. The woman now claims to be one of the types, and may send a signal to say, for example, that they are a heavy drinker. We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred. We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one.

\begin{figure}[H]
\includegraphics[width=\textwidth]{figures/less_simplest_game}
\caption{A less simple two player signalling game. }

@@

\begin{figure}[H]
\subfloat[Women (heavy drinkers)]{\includegraphics[width=11.9cm]{figures/women_influence}}
\vskip\baselineskip
\subfloat[Midwives]{\includegraphics[width=11.9cm]{figures/mw_influence}}
\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
